---
title: "ShinyApp"
author: "Neeraj Agarwal"
date: "July 28, 2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Overview

Create an Shiny Application and deploy it on RStudio Server. This peer assessed assignment has two parts. 

- Create a Shiny application and deploy it on Rstudio's servers. 
- Use Slidify or Rstudio Presenter to pitch reproducible presentation about the application.

## Application Overview

This shiny app takes the two years of incident data for multiple applications from an application maintenance project and publish the histogram for individual selected applications. 
Input for the histogram is application and Shiny app shows the incident count per month both in histogram and in a table.

## Links

- Data: Data is uploaded on Gits Hub to refer and download. This data has Incident details which includes, Incident number, Incident raised on Resolved date, status and Application.
https://raw.githubusercontent.com/Neerajagar/ShinyApp/master/incidents.csv

- Shiny App: Shiny App is published on the below link.

https://neerajagr.shinyapps.io/ShinyApp/

- Shiny App Files: Both ui & server files are uploaded in Github.



## Slide with Plot

```{r incidentdata, message=FALSE, warning= FALSE}

library(readr)
library(shiny)
library(plotly)
library(lubridate)
library(dplyr)
library(ggplot2)

all_incidents <- read.csv("https://raw.githubusercontent.com/Neerajagar/ShinyApp/master/incidents.csv",header = TRUE,stringsAsFactors = F) 

incidents <- data.frame(all_incidents$Number,all_incidents$application,format(as.POSIXct(all_incidents$Opened,format="%Y-%m-%d"),"%Y-%m"))

names(incidents) <- c("Number","Application","Opened")

incidents <-incidents %>% count(Application, Opened)

#Total Recors:
dim(incidents)

# Sample Records
head(incidents)
```

